### 2020-11-18 ch01_introduction/introduction.tex
Added first figure

\chapter{Introduction}
\label{ch:introduction}

The \ac{ECS} is really cool. I like it very much!

>>>>

\chapter{Introduction}
\label{ch:01:introduction}

\section{Structure of the thesis}
\label{sec:01:structure}

Parts of this thesis are published in multiple scientific publications (two as
first author six as co-author). If applicable, this is clearly stated at the
beginning of each chapter. \Cref{ch:02:scientific_background} introduces the
scientific background for this thesis. This includes basic principles of Earth
System Modeling, sources of uncertainty in future projections of the climate,
relevant definitions and state-of-the-art methods used to evaluate \ac{ESM}
simulations and reduce associated uncertainties. \Cref{ch:03:esmvaltool} gives
an overview over the contributions made to the \ac{ESMValTool}, an open-source
software for the analysis of \acp{ESM}. These contributions helped improving
the routine evaluation of \acp{ESM} which is useful for the whole scientific
community and lead to co-authorship in four peer-reviewed studies
\autocite{Righi2020, Eyring2020, Lauer2020, Weigel2020}.
\Cref{ch:04:assessment_climate_metrics} covers the assessment of
policy-relevant climate metrics like the \ac{EqCS} and the \ac{TCR} in the
latest generation of \acp{ESM}. This work is already published in two
scientific publications \autocite{Bock2020, Meehl2020}. Since the \ac{EqCS} and
\ac{TCR} are considerably higher in this new climate model generation,
\cref{ch:05:paper_ecs} describes the assessment of emergent constraints (a
technique to reduce uncertainties in climate model projections, see
\vref{sec:02:techniques}) on the \ac{EqCS} for these \acp{ESM}. The contents of
this chapter are published in \emph{Earth System Dynamics}
\autocite{Schlund2020a}. \Cref{ch:06:paper_gpp} focuses on a new method to
reduce climate model uncertainties based on \ac{ML}. As an example, the method
is applied to the photosynthesis rate at the end of the \nth{21} century, which
is already published in the \emph{Journal of Geophysical Research:
Biogeosciences} \autocite{Schlund2020}. Finally, \cref{ch:07:summary_outlook}
provides a summary of the results of this thesis and gives an outlook of
possible future works.

### 2020-11-18 ch02_scientific_background/scientific_background.tex
Initialized chapters
Wrote first page of introduction
Added first figure

%=============================================================================%
%                                Dissertation                                 %
%                               Manuel Schlund                                %
%                                  (c) 2020                                   %
%=============================================================================%
%                                Introduction                                 %
%=============================================================================%

\chapter{Introduction}
\label{ch:introduction}

The \ac{ECS} is really cool. I like it very much!

>>>>

%=============================================================================%
%                                Dissertation                                 %
%                               Manuel Schlund                                %
%                                  (c) 2020                                   %
%=============================================================================%
%                            Scientific Background                            %
%=============================================================================%

\chapter{Scientific Background}
\label{ch:02:scientific_background}

\section{Earth System Models: Simulations and Analysis}
\label{sec:02:esms}

An \ac{ESM} is really cool! Yes, \acp{ESM}!!

\begin{figure}[t]
  \centering
  \includegraphics[width=\figureWidth{}]{
    ch02_scientific_background/figs/esms_historical_evolution.pdf}
  \caption{Historical evolution of coupled climate models over the last 45
  years. In early days, these models were \acfp{AOGCM} and only included three
  components: the atmosphere, the land surface and the ocean. Over the time,
  the individual components grew in complexity and included a wider range of
  processes (illustrated by the growing cylinders). Eventually, more and more
  components (aerosols, carbon cycle, \etc{}) were added to the coupled system,
  forming the modern \acfp{ESM}. Taken from \textcite{Cubasch2013}.}
  \label{fig:02:esms_historical_evolution}
\end{figure}

TBA.

\section{Techniques to reduce uncertainties in climate model projections}
\label{sec:02:techniques}

### 2020-11-18 end_acronyms/acronyms.tex
Added first figure

\begin{acronym}
  \acro{CMIP}{Coupled Model Intercomparison Project}
  \acro{CMIP3}{Phase 3 of the Coupled Model Intercomparison Project}
  \acro{CMIP5}{Phase 5 of the Coupled Model Intercomparison Project}
  \acro{CMIP6}{Phase 6 of the Coupled Model Intercomparison Project}
  \acro{DLR}{
    Deutsches Zentrum für Luft- und Raumfahrt (German Aerospace Center)}
  \acro{ECS}{Effective Climate Sensitivity}
  \acro{ESM}{Earth System Model}
  \acro{ESMValTool}{Earth System Model Evaluation Tool}
  \acro{EqCS}{Equilibrium Climate Sensitivity}
  \acro{GPP}{Gross Primary Productivity}
  \acro{IPA}{
    Institut für Physik der Atmosphäre (Institute of Atmospheric Physics)}
  \acro{MIP}{Model Intercomparison Project}
  \acro{ML}{Machine Learning}
  \acro{TCR}{Transient Climate Response}
\end{acronym}

>>>>

\begin{acronym}
  \acro{AOGCM}{Atmosphere-Ocean General Circulation Model}
  \acro{CMIP}{Coupled Model Intercomparison Project}
  \acro{CMIP3}{Phase 3 of the Coupled Model Intercomparison Project}
  \acro{CMIP5}{Phase 5 of the Coupled Model Intercomparison Project}
  \acro{CMIP6}{Phase 6 of the Coupled Model Intercomparison Project}
  \acro{DLR}{%
    Deutsches Zentrum für Luft- und Raumfahrt (German Aerospace Center)}
  \acro{ECS}{Effective Climate Sensitivity}
  \acro{ESM}{Earth System Model}
  \acro{ESMValTool}{Earth System Model Evaluation Tool}
  \acro{EqCS}{Equilibrium Climate Sensitivity}
  \acro{GPP}{Gross Primary Productivity}
  \acro{IPA}{%
    Institut für Physik der Atmosphäre (Institute of Atmospheric Physics)}
  \acro{MIP}{Model Intercomparison Project}
  \acro{ML}{Machine Learning}
  \acro{TCR}{Transient Climate Response}
\end{acronym}
